\chapter*{Abstract}
\noindent \indent MUTW stands for Multinational Undergraduate Team Work. The
goal of MUTW is to let students of eleven different universities work together on one common project. The assignment of this year was to implement the ErasmusLine web application. The purpose of this application was to digitalize the complete Erasmus process, so that students who want to go on Erasmus didn’t have to fill in all the forms by hand, butt everything would happen digitally.
\ \\
\indent  The eleven universities taken part in this project were separated into
two teams, namely team Orange and team Blue. Those two teams would then work for about three months on implementing the application and at the end of those three months, they would have to give a presentation with their final result.
\ \\
\indent The implementation of the application itself was divided in eight
modules, which were distributed among the universities in each team. By dividing this project in different modules, each university could work independently on their own module, but this made the communication part of the project very important. Although each university could work independently on their modules, nevertheless did some modules depend on others.
\ \\
\indent The web application was written in XHTML with PHP as server-side
scripting language. Besides XHMTL and PHP, the Orange Team also used the MySQL
database as a data layer and JavaScript/jQuery as client-side scripting
language. The course-matching module used the Python programming language. 
\ \\ 
\indent This assignment was a very enriching experience for the whole team.
During the implementation of the ErasmusLine web application, some issues were
encountered and bugs to fix, but eventually a working application was presented
at the final meeting in Heraklion, Greece.

\section*{Keywords}
Database, data-management, user-management, sql, security-levels, homepage,
main- menu, privileges, permissions, interoperability, interface, data transfer,
file transfer, encryption, security, JSON, 3DES, cURL, Erasmus, forms,
server-side, validation, client-side, persistence, process
flow, signatures, exams, interface, institution, coordinator, student,
statistics, analytics, trends, charts, pivot tables, data warehouse,data
refreshment, executive information system, EIS, online analytical processing,
OLAP, extract transform load, ETL, data mining, facts, dimensions, measures,
posix, daemon, mysql, php, html, jquery.
